\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-02-16 paper.tex
Add abstract

>>>>

Band Protocol is a decentralized, permissionless blockchain protocol to create tokenized marketplace and token-curated community. Band Protocol enables seamless issuance of personalized Community Token through a continuous bonding curve, a smart contract that mints and burned personalized token through a predefined mathematical function based on current circulating supply. Any entities ranging from businesses, brands and celebrities can create a loyal token-curated community with personalized tokens. Personalized Community Token is a utility token representing primary currency, subscription, discount, reward point, or any other use cases within the community as defined by the Community Manager.

Band Protocol standardizes Product Token as a way for community manager to issue products and services. It enables both tokenized real-world products as well as new digital asset creation such as rare digital collectibles and attention token.

Band Protocol enables the creation of subscription business model. Followers can stake their Community Token to a staking contract and receive regular benefits similar to normal subscription or membership. Band Protocol allows Community Manager to define their subscription tier and discount token. Discount token is a tokenized discount voucher used to reward loyal followers and incentivize active participants rather than speculators. The amount of discounts can be customized by Community Manager and in general is proportionate to the amount of total network value. Discount tokens will be an incentive for loyal followers to stake their tokens and promote the growth of the community.

Band Token is the native utility token on the delegated-proof-of-stake Band Chain. Band Token are used to secure the network, provide global liquidity to every Community Token, and act as a governance token for future protocol upgrade.
